Incentivizing Exploration with Heterogeneous Utilities

### 2017-11-28 paper.tex
fixed our assumption 1

In the calculation below, we omit the dependency on $\omega$ when refering to variables $c(t)$ and $t_n$. Based on the definition of $L[l]$, we know if $\omega\in L[l]$, the maximum payment we need to offer at time $t$ is bounded above by 
\begin{align}
&\max_{i}\theta_t\cdot u_{i,t} - \min_{j}\theta_t\cdot u_{j,t} \nonumber \\
= &\max_{i}\theta_t\cdot (\epsilon_{i,t}+u_i) - \min_{j}\theta_t\cdot (\epsilon_{j,t}+u_j) \nonumber \\
\leq &\max_{i}\theta_t\cdot u_i - \min_{j}\theta_t\cdot u_j +\max_{i}\theta_t\cdot \epsilon_{i,t} - \min_{j}\theta_t\cdot \epsilon_{j,t}\nonumber \\
\leq & R + 2Wmg(n,l). \nonumber
\end{align}

@@

\begin{align}
&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}E[c(t)|\omega \in L[l],t\in [t_n,t_{n+1}))P(\omega\in L[l],t\in [t_n,t_{n+1})) \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}\left[R+2Wm\frac{l}{n}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}\left[R+2Wm\frac{l}{n}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))Nn. \nonumber
\end{align}

We now bound $P(\omega\in L[l]|t\in[t_{n},t_{n+1}))$. \bccomment{Is my calculation to bound this probability correct?}
\begin{align}
&P(\omega\in L[l]|t\in[t_{n},t_{n+1})) \nonumber \\
=&P(\omega\in L^{'}[l]|t\in[t_{n},t_{n+1}))- P(\omega\in L^{'}[l-1]|t\in[t_{n},t_{n+1})) \nonumber \\
=&P(|\epsilon_{i,t}^{j}|<\frac{l}{n}, \forall i,j|t\in[t_n,t_{n+1}))-P(|\epsilon_{i,t}^{j}|<\frac{l-1}{n}, \forall i,j|t\in[t_n,t_{n+1})) \nonumber \\
=&\Pi_{i=1}^{N}\Pi_{j=1}^{m}P\left(|\epsilon_{i,t}^{j}|<\frac{l}{n}|t\in[t_n,t_{n+1})\right)-\Pi_{i=1}^{N}\Pi_{j=1}^{m}P\left(|\epsilon_{i,t}^{j}|<\frac{l-1}{n}|t\in[t_n,t_{n+1})\right). \label{prob:upper}
\end{align}
Since we are at round $n$, we know there exists at least one arm, which has been pulled exactly $n$ times. Without loss of generality, we assume it to be arm $1$. Since $P\left(|\epsilon_{i,t}^{j}|<\frac{l}{n}|t\in[t_n,t_{n+1})\right)> P\left(|\epsilon_{i,t}^{j}|<\frac{l-1}{n}|t\in[t_n,t_{n+1})\right)$ for all $i,j$, we know

>>>>

In the calculation below, we omit the dependency on $\omega$ when refering to variables $c(t)$, $\epsilon_{i,t}^{j}$ and $t_n$. Based on the definition of $L[l]$, we know if $\omega\in L[l]$, the maximum payment we need to offer at time $t$ is bounded above by 
\begin{align}
&\max_{i}\theta_t\cdot u_{i,t} - \min_{j}\theta_t\cdot u_{j,t} \nonumber \\
= &\max_{i}\theta_t\cdot (\epsilon_{i,t}+u_i) - \min_{j}\theta_t\cdot (\epsilon_{j,t}+u_j) \nonumber \\
\leq &\max_{i}\theta_t\cdot u_i - \min_{j}\theta_t\cdot u_j +\max_{i}\theta_t\cdot \epsilon_{i,t} - \min_{j}\theta_t\cdot \epsilon_{j,t}\nonumber \\
\leq & R + 2Wmg(n,l). \nonumber
\end{align}

@@

\begin{align}
&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}E[c(t)|\omega \in L[l],t\in [t_n,t_{n+1}))P(\omega\in L[l],t\in [t_n,t_{n+1})) \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}\left[R+2Wm\frac{l}{n}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})). \nonumber
\end{align}

We now bound $P(\omega\in L[l]|t\in[t_{n},t_{n+1}))$.
\begin{align}
&P(\omega\in L[l]|t\in[t_{n},t_{n+1})) \nonumber \\
=&P(\omega\in L^{'}[l]|t\in[t_{n},t_{n+1}))- P(\omega\in L^{'}[l-1]|t\in[t_{n},t_{n+1})) \nonumber \\
\leq & 1-P(|\epsilon_{i,t}^{j}|<\frac{l-1}{n}, \forall i,j|t\in[t_n,t_{n+1})) \nonumber \\
=&P(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{l-1}{n}|t\in[t_n,t_{n+1})) \nonumber  \\
=&\sum_{i,j}P(|\epsilon_{i,t}^{j}|\geq \frac{l-1}{n}|t\in[t_n,t_{n+1})) \nonumber \\
=&\sum_{i,j}P(|S_{i,t}^{j}|\geq \frac{N(i,t)(l-1)}{n}|t\in[t_n,t_{n+1})) \nonumber 
\end{align}

Since we are at round $n$, we know there exists at least one arm, which has been pulled exactly $n$ times. Without loss of generality, we assume it to be arm $1$. Since $P\left(|\epsilon_{i,t}^{j}|<\frac{l}{n}|t\in[t_n,t_{n+1})\right)> P\left(|\epsilon_{i,t}^{j}|<\frac{l-1}{n}|t\in[t_n,t_{n+1})\right)$ for all $i,j$, we know
